The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2019-03-12 paper/ms.tex
github link
bad stars text

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/k2halo}{\faGithub}
\end{abstract}

@@

To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification code \citep[SPC:][]{spc} to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff was fixed from the results of an initial SPC fit, while \logg was fixed to the seismic values. The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}. The results from this calculation are displayed in Table~\ref{stellar_props}. BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}. For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation). Additionally, we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T. Masseron, private communication). The SiH molecular information was adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B. Plez (private communication).

>>>>

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
\end{abstract}

@@

To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification code \citep[SPC:][]{spc} to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax. For deriving abundances, \teff was fixed from the results of an initial SPC fit, while \logg was fixed to the seismic values. For four stars with low \logg and metallicity (BD+43~3171, HD~174020, HD~180682, and HD~181022), the stellar spectral templates in SPC gave unsatisfactory fits. In these cases, \teff was fixed to the results of a broadband spectral energy distribution (SED) fit to archival photometry as catalogued by \citet{Mcdonald2017}, and \logg calculated from these without iteration.

The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}. The results from this calculation are displayed in Table~\ref{stellar_props}. BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}. For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation). Additionally, we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T. Masseron, private communication). The SiH molecular information was adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B. Plez (private communication).
